HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-08-09 scnn.tex
update filter figure
four tasks: global and dense classification and prediction

    \item (MD+NP) talk about the loss in 2.8 (old 4.8) \nati{I was very brief. In color for now.}
    \item (done!) (NP) make figure A.13 remove white space
    \item (first version done!)(NP+MD) paragraph on our chosen architecture in the Experiments sections
    \item (Done) (NP) vertex interpretation 
    \item (MD) Are you happy with the vertex interpretation in section 2.5 Efficient convolutions? Also do you like the end of 2.4?
    \item (NP) Finalise readme on Github code
    \item branch with notebooks with plots (results) NP
    \item NP move the repo to HealpixNet
    \item check if papers which appear as arxiv were not published in a conference or journal
    \item MD add irregular (random) sampling to comparison with spherical harmonics? Could motivate people to think about different samplings. \nati{I think this is too much for this paper.}
    \item TK check part sphere notebook and whole sphere
    \item (done!) (TK) update the README for data zip - file from NP
    \item (almost done) TK read everything
    \item (done!) (TK) uniformize text size in figures
    \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook. \nati{We need to talk about that.}
    \item (done!) (TK) re-make figures to make the labels/legend/titles the same font size as the main text
    \item (done!) TK check the appendix
    \item (done!) TK optional - example of data (CMB (mask) + mass map + radio intensity)
    \item (done!) (TK) add info on comparison with histograms, so that it's just a demonstration
    \item (done!) TK read the result section
    \item (done!) (TK) add reference to figure (pooling) to the area of orders
    \item (done!) (TK) add section in conclusions/ paragraph on possible extensions to the code: dense output, regression, GANs, segmentation
	\item Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
    \item Check names: HealpixNet, HealpixCNN, HealpixFCN
    \item Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
    % \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
    % \item (done! first version done) conclusions
    % \item (done!) Michael section 4.5 (efficient convolutions) and 3.2 (conv on graphs)
    % \item (done!) (TK NP) if we have time make a new candidate for network plot (optional)
    % \item (done!) TK read the heat section again
    % \item (done!) (TK) make a new proposition for a plot Figure 6: Two levels of coarsening and pooling
    % \item \todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
    % Nati: I did it without this notation. Since we have two architectures, I think it is OK.
\end{itemize}

@@

To overcome those shortcomings, we introduce an efficient spherical CNN formulation which uses (i) convolutions on graphs and (ii) hierarchical pooling.
The main idea is to represent the sphere $S^2$, a 2-dimensional manifold embedded in $\mathbb{R}^3$, as a graph of connected pixels.
The length (or weight) of the shortest path between two pixels is an approximation of the geodesic distance between them on the manifold.
The use of this approach is enabled by recent developments in graph signal processing, where fundamental tools, such as for example the Fourier transform, were defined \citep{shuman2013emerging} for graphs.
Our approach uses the graph CNN formulation introduced by \citet{defferrard2016convolutional}, which can be adapted to any sampling of the sphere.
Using a $k$-nearest neighbours graph, the convolution operation costs $\mathcal{O}(N_{pix})$ operations, where $N_{pix}$ is the number of pixels.
This is the lowest possible complexity for a convolution operation without approximations (e.g. by sketching).
The flexibility of modelling the data domain with a graph allows to easily model data that spans only a part of the sphere, or data that is not uniformly sampled.
Our hierarchical pooling strategy exploits a hierarchical pixelisation of the manifold to analyse the data at multiple scales.
% Such hierarchical pixelisations of the sphere have been well studied.

In this work we present and release HealpixNet\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}, an algorithm and software package which implements an efficient CNN on HEALPix maps. It is implemented with \pkg{TensorFlow} \citep{abadi2016tensorflow} and is intended to be easy to use out-of-the box for cosmological applications.
As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology and astrophysics, we tailored our method to that particular sampling.
The elements of the graph that depend on the sampling are:
(i) the choice of neighboring pixels when building the graph, and
(ii) the choice of parent pixels when building the hierarchy of layers.
% It is also possible to use multiple HEALPix maps within our framework and use datasets in form of ``shells''.
% These shells can span the radial direction, so that a tomographic analysis can be performed, or different frequencies, in case of data from observations in radio frequencies.
% \nati{I do not know about that last point. Yes we can do it. But a) we did not do it and b) the filter will be spherical in all directions includeding the radial one... I am not sure this is a disirable features.}
% \todo{I think you got it wrong there. I guess the idea is that each shell would be a feature map, i.e., the graph signal would be multi-dimensional.}
% \TK{OK, let's talk about it.}
%\nati{I am not sure this goes there...} Other recently developed sampling methods include \citep{mcewen2011novelsampling}, where exact sampling theorem for equiangular MW sampling was presented.

@@

Given a map $\X \in \R^{N_{pix} \times F}$, the neural network is computing $\y = NN_\theta(\X) \in R^{N_{classes}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
An example network is
\begin{equation*}
NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC,
\end{equation*}
where $\circ$ denotes composition, i.e., $f \circ g = f(g(\cdot))$.
The number of features $F$ depends on the data at hand. For the CMB radiation temperature, $F = 1$. For observations in radio frequencies, $F$ would be equal to the number of surveyed frequencies. $F$ might also be the number of slices in the radial direction.
The loss function $\ell(\y) = \ell(NN_\theta(\X))$ is a measure of how good the prediction $\y$ is for the sample $\X$. For a classification task, the loss is usually taken to be the cross-entropy
\begin{equation*}
	\ell(\y) = -\log(y_i),
\end{equation*}
where $i$ is the correct class label.
\todo{For a regression task, the most common choice is the $L^2$ norm $\ell(\y) = \|\y-\bar{\y}\|_2^2$, where $\bar{\y}$ is the desired output, as it minimize the mean square error. We emphasis that by sole change of the loss, one can solve regularization instead of classification.}

The parameters $\theta$ of the neural network are optimized to minimize the loss over the training dataset $\left\{ \X_i \right\}_{i=1}^{N_{samples}}$:
\begin{equation*}
	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} \ell(NN_\theta(\X_i)).
\end{equation*}
The same architecture with different loss function can also be used for parameter regression \citep{fluri2018deep,gupta2018nongaussianinformation}.
The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
\begin{equation*}
	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
\end{equation*}
where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch. Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.

@@

\subsection{Selected architecture}
The choice of a particular HealPixNet architecture highly depends on the problem at hand. Convolution layers construct \emph{almost} rotational equivariant features and the statistical layer can turn them into rotational invariant ones. In our case, we are trying to discriminate samples of two cosmological maps. Hence, we assume that each pixel carries some information about the distribution. Our principal architecture is a fully convolutional network referred as HealPixFCN. Thanks to 6 graph convolution layers (GC sizes: 16, 32, 64, 64, 64, 2) we first build the statistical evidence of each distribution for each pixel of a down-sampled sphere. The last graph convolution layer is composed of 2 channels as we have 2 distributions. Then we use a statistical 'mean' layer (SL) to average the evidence for each distribution and we compute the probabilities thanks to a softmax layer (SM). We use batch normalization (BN), pooling (P) and relu non-linearity $\sigma$ for each convolutional layer. The network can be summarized as
\begin{equation}
FCN = SM \circ ST_{\text{mean}} \circ L_6 \circ L_5 \circ L_4 \circ L_3 \circ L_2 \circ L_1
\end{equation}
\begin{center}
where \hspace{0.5cm} \begin{tabular}{lll}
   $L_1$ &  $=$ &$ P  \circ \sigma \circ BN  \circ GC_{16}$ \\
   $L_2$ &  $=$ &$ P  \circ \sigma \circ BN  \circ GC_{32}$ \\
   $L_3,L_4,L_5$ & $=$ &$ P \circ  \sigma \circ BN  \circ GC_{64}$ \\
   $L_6$ &  $=$& $ \sigma \circ BN  \circ GC_{2}$ \\
\end{tabular}
\end{center}
Thanks to its statistical layer, the FCN architecture is close invariant to rotation.
We also tried a more traditional architecture, where the statistical and last convolutional layers are replaced by a fully connected layer. Hence we end up with a convolutional neural network (CNN) that is not invariant to rotation anymore. The network is referred as HealPixCNN and can be summarized as
\begin{equation}
CNN = SM \circ \sigma \circ FC_2 \circ L_5 \circ L_4 \circ L_3 \circ L_2 \circ L_1.
\end{equation}
We use the ADAM optimizer, \cite{kingma2014adam}, with $\beta_1=0.9$, $\beta_2=0.999$ and an initial learning rate of $2e-4$ that is exponentially decreased by $0.999$ at each step.
All models were trained $80$ epochs with a batch size of $16\times o^2$. With this choice, all models receive an identical amount of data within a batch and were trained with $1920$ gradient steps.
Training took less than $5$ hours for each model using a single NVIDIA Tesla K20.
% The CPU is probably slow which explain the 5 hours. I believe we could be much faster than that by computer less summaries and improving the data. But, Michael, is OKAY to have to margin of improvement :-)

@@

\subsection{Filter visualization}
One common visualization for CNN is to observe the shape of the learned filters.
Since our construction leads to almost (up to the sampling irregularities) spherical filters, we plot in \figref{learned_filter} both the radial profile and a gnomonic projection on a plane of a random selection of learned filters.
The filters are selected from the last layer of the network corresponding the experiment with order $o=2$ for a relative noise level of $2$.
Nevertheless, all networks presented visually similar gnomonic and profile patterns.
% The gnomonic projection clearly exibits the sampling issue of HEALPix.
% \TK{what issue? Commenting out for now}
Details of how the convolution kernels are plotted are described in \ref{sec:filter_visualization}.
While it is usually difficult to interpret the shape of the filters in the context of the type of data, we can notice that they often have a ``peak'' like structures.
An example of filter interpretation was demonstrated in \citep{Ribli2018learningfrom}.
% \todo{Tomek: can you say something about the filters.}
% \TK{Done}

>>>>

	\item (MD) distinction between CNN and FCN
    \item (done!) (NP) make figure A.13 remove white space
    \item (first version done!)(NP+MD) paragraph on our chosen architecture in the Experiments sections
    \item (Done) (NP) vertex interpretation 
    \item (MD) Are you happy with the vertex interpretation in section 2.5 Efficient convolutions? Also do you like the end of 2.4?
    \item (NP) Finalise readme on Github code
    \item branch with notebooks with plots (results) NP
    \item NP move the repo to HealpixNet
    \item check if papers which appear as arxiv were not published in a conference or journal
    \item MD add irregular (random) sampling to comparison with spherical harmonics? Could motivate people to think about different samplings. \nati{I think this is too much for this paper.}
    \item TK check part sphere notebook and whole sphere
    \item (done!) (TK) update the README for data zip - file from NP
    \item (almost done) TK read everything
    \item (done!) (TK) uniformize text size in figures
    \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook. \nati{We need to talk about that.}
    \item (done!) (TK) re-make figures to make the labels/legend/titles the same font size as the main text
    \item (done!) TK check the appendix
    \item (done!) TK optional - example of data (CMB (mask) + mass map + radio intensity)
    \item (done!) (TK) add info on comparison with histograms, so that it's just a demonstration
    \item (done!) TK read the result section
    \item (done!) (TK) add reference to figure (pooling) to the area of orders
    \item (done!) (TK) add section in conclusions/ paragraph on possible extensions to the code: dense output, regression, GANs, segmentation
	\item Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
    \item Check names: HealpixNet, HealpixCNN, HealpixFCN
    \item Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
    % \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
    % \item (done! first version done) conclusions
    % \item (done!) Michael section 4.5 (efficient convolutions) and 3.2 (conv on graphs)
    % \item (done!) (TK NP) if we have time make a new candidate for network plot (optional)
    % \item (done!) TK read the heat section again
    % \item (done!) (TK) make a new proposition for a plot Figure 6: Two levels of coarsening and pooling
    % \item \todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
    % Nati: I did it without this notation. Since we have two architectures, I think it is OK.
\end{itemize}

@@

To overcome those shortcomings, we introduce an efficient spherical CNN formulation which uses (i) convolutions on graphs and (ii) hierarchical pooling.
The main idea is to represent the sphere $S^2$, a 2-dimensional manifold embedded in $\mathbb{R}^3$, as a graph of connected pixels.
The length (or weight) of the shortest path between two pixels is an approximation of the geodesic distance between them on the manifold.
The use of this approach is enabled by recent developments in graph signal processing, where fundamental tools, such as for example the Fourier transform, were defined \citep{shuman2013emerging} for graphs.
Our approach uses the graph CNN formulation introduced by \citet{defferrard2016convolutional}, which can be adapted to any sampling of the sphere.
Using a $k$-nearest neighbours graph, the convolution operation costs $\mathcal{O}(N_{pix})$ operations, where $N_{pix}$ is the number of pixels.
This is the lowest possible complexity for a convolution operation without approximations (e.g. by sketching).
The flexibility of modeling the data domain with a graph allows to easily model data that spans only a part of the sphere, or data that is not uniformly sampled.
Our hierarchical pooling strategy exploits a hierarchical pixelisation of the manifold to analyse the data at multiple scales.
% Such hierarchical pixelisations of the sphere have been well studied.

In this work we present and release HealpixNet\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}, an algorithm and software package which implements an efficient CNN on HEALPix maps. It is implemented with \pkg{TensorFlow} \citep{abadi2016tensorflow} and is intended to be easy to use out-of-the-box for cosmological applications.
HealpixNet is readily apt to solve four tasks: (i) global classification (i.e., predict a class from a map), (ii) global regression (i.e., predict a set of parameters from a map), (iii) dense classification (i.e., predict a class for each pixel of a map), and (iv) dense regression, (i.e., predict a set of maps from a map).
As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology and astrophysics, we tailored our method to that particular sampling.
The elements of the graph that depend on the sampling are:
(i) the choice of neighboring pixels when building the graph, and
(ii) the choice of parent pixels when building the hierarchy of layers.
% It is also possible to use multiple HEALPix maps within our framework and use datasets in form of ``shells''.
% These shells can span the radial direction, so that a tomographic analysis can be performed, or different frequencies, in case of data from observations in radio frequencies.
% \nati{I do not know about that last point. Yes we can do it. But a) we did not do it and b) the filter will be spherical in all directions includeding the radial one... I am not sure this is a disirable features.}
% \todo{I think you got it wrong there. I guess the idea is that each shell would be a feature map, i.e., the graph signal would be multi-dimensional.}
% \TK{OK, let's talk about it.}
%\nati{I am not sure this goes there...} Other recently developed sampling methods include \citep{mcewen2011novelsampling}, where exact sampling theorem for equiangular MW sampling was presented.

@@

Given a map $\X \in \R^{N_{pix} \times F_{in}}$, a neural network for global prediction is computing $\y = NN_\theta(\X) \in R^{F_{out}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
Two example networks for global classification, a CNN and a FCN, are
\begin{align*}
	NN &= SM \circ FC \circ \sigma \circ FC \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC, \\
	NN &= \underbrace{SM \circ ST \circ \sigma \circ GC}_{\text{classifier}} \circ \underbrace{\sigma \circ GC \circ P \circ \sigma \circ BN \circ GC}_{\text{feature extractor}},
\end{align*}
where $\circ$ denotes composition, i.e., $(f \circ g)(x) = f(g(x))$.
The number of features $F_{in}$ depends on the data at hand. For the CMB radiation temperature, $F_{in} = 1$. For observations in radio frequencies, $F_{in}$ would be equal to the number of surveyed frequencies. $F_{in}$ might also be the number of slices in the radial direction. The number of predictions $F_{out}$ is either equal to the number of classes $N_{classes}$ for a classification task, or the number of variables to be predicted for a regression task. A typical global classification task is to classify maps into cosmological model classes \citep{schmelze2017cosmologicalmodel}. A typical global regression task is to infer the parameters of a cosmological model  from maps \citep{fluri2018deep,gupta2018nongaussianinformation}.
Dense prediction, i.e., predicting $F_{out}$ values per pixel, is obtained by omitting ST and FC layers (P layers, if used, have to be inverted via up-sampling in an encoder-decoder architecture). An example network for dense regression is
\begin{equation*}
	\Y = NN(\X) = (GC \circ \sigma \circ BN \circ GC)(\X) \in \R^{N_{pix} \times F_{out}}.
\end{equation*}
Such networks are useful for (i) dense regression, such as denoising a map, interpolating missing values, or predicting a density map given the CMB, or (ii) dense classification, such as segmenting galactic clusters in a \todo{xx} map. \todo{TK: please find better cosmological applications. Maybe some refs?} We emphasize that the use of FC and ST layers is the sole difference between a neural network engineered for global or dense prediction.

The loss function $\ell(\Y, \bar \Y) = \ell(NN_\theta(\X), \bar \Y)$ measures how good the prediction $\Y$ is for sample $\X$, given the ground truth $\bar \Y$. For a classification task, the loss is usually taken to be the cross-entropy
\begin{equation*}
	\ell(\Y, \bar \Y) = - \sum_{i=1}^{N_{pix}} \sum_{j=1}^{N_{classes}} \bar y_{ij} \log(y_{ij}),
\end{equation*}
where $\bar \Y \in \R^{N_{pix} \times N_{classes}}$ is the ground truth label indicator, i.e., $\bar y_{ij} = 1$ if pixel $i$ of sample $\X$ belongs to class $j$ and is zero otherwise. For global prediction, the loss is as if $N_{pix} = 1$.
For a regression task, a common choice is the mean squared error (MSE)
\begin{equation*}
	\ell(\Y, \bar \Y) = \frac{\|\Y-\bar{\Y}\|_2^2}{N_{pix} F_{out}} = \frac{1}{N_{pix} F_{out}} \sum_{i=1}^{N_{pix}} \sum_{j=1}^{F_{out}} (y_{ij} - \bar y_{ij})^2,
\end{equation*}
where $\bar{\Y}$ is the desired output. Again, take $N_{pix} = 1$ for global regression. We emphasize that the loss and the SM layer is the sole difference between a neural network engineered for classification or regression.

The goal of learning is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = \esp \left[ \ell \left( NN_\theta(\X), \bar \Y \right) \right]$. In general, that expectation cannot be computed as the data distribution is unknown. We can however minimize an approximation, the empirical risk over the training set $\left\{ \left( \X_i, \bar \Y_i \right) \right\}_{i=1}^{N_{samples}}$:
\begin{equation*}
	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} \ell \left(NN_\theta(\X_i), \bar \Y_i \right).
\end{equation*}
The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
\begin{equation*}
	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell \left( NN_\theta(\X_i), \bar \Y_i \right)}{\partial \theta} ,
\end{equation*}
where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch. Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.

@@

\subsection{Selected architecture}
The choice of a particular HealPixNet architecture highly depends on the problem at hand. Convolution layers construct \emph{almost} rotational equivariant features and the statistical layer can turn them into rotational invariant ones. In our case, we are trying to discriminate samples of two cosmological maps. Hence, we assume that each pixel carries some information about the distribution. Our principal architecture is a fully convolutional network referred as HealPixFCN. Thanks to 6 graph convolution layers (GC sizes: 16, 32, 64, 64, 64, 2) we first build the statistical evidence of each distribution for each pixel of a down-sampled sphere. The last graph convolution layer is composed of 2 channels as we have 2 distributions. Then we use a statistical 'mean' layer (SL) to average the evidence for each distribution and we compute the probabilities thanks to a softmax layer (SM). We use batch normalization (BN), pooling (P) and relu non-linearity $\sigma$ for each convolutional layer. The order of the convolution kernel was set to $K=5$. The network can be summarized as
\begin{equation}
FCN = SM \circ ST_{\text{mean}} \circ L_6 \circ L_5 \circ L_4 \circ L_3 \circ L_2 \circ L_1
\end{equation}
\begin{center}
where \hspace{0.5cm} \begin{tabular}{lll}
   $L_1$ &  $=$ &$ P  \circ \sigma \circ BN  \circ GC_{16}$ \\
   $L_2$ &  $=$ &$ P  \circ \sigma \circ BN  \circ GC_{32}$ \\
   $L_3,L_4,L_5$ & $=$ &$ P \circ  \sigma \circ BN  \circ GC_{64}$ \\
   $L_6$ &  $=$& $ \sigma \circ BN  \circ GC_{2}$ \\
\end{tabular}
\end{center}
Thanks to its statistical layer, the FCN architecture is close invariant to rotation.
We also tried a more traditional architecture, where the statistical and last convolutional layers are replaced by a fully connected layer. Hence we end up with a convolutional neural network (CNN) that is not invariant to rotation anymore. The network is referred as HealPixCNN and can be summarized as
\begin{equation}
CNN = SM \circ \sigma \circ FC_2 \circ L_5 \circ L_4 \circ L_3 \circ L_2 \circ L_1.
\end{equation}
We use the ADAM optimizer, \cite{kingma2014adam}, with $\beta_1=0.9$, $\beta_2=0.999$ and an initial learning rate of $2e-4$ that is exponentially decreased by $0.999$ at each step.
All models were trained $80$ epochs with a batch size of $16\times o^2$. With this choice, all models receive an identical amount of data within a batch and were trained with $1920$ gradient steps.
Training took less than $5$ hours for each model using a single NVIDIA Tesla K20.
% The CPU is probably slow which explain the 5 hours. I believe we could be much faster than that by computer less summaries and improving the data. But, Michael, is OKAY to have to margin of improvement :-)

@@

\subsection{Filter visualization}
One common visualization for CNN is to observe the shape of the learned filters.
Since our construction leads to almost (up to the sampling irregularities) spherical filters, we plot in \figref{learned_filter} both the radial profile and a gnomonic projection on a plane of a random selection of learned filters.
The filters are selected from the last layer of the network corresponding the experiment with order $o=2$ for a relative noise level of $2$.
Nevertheless, all networks presented visually similar gnomonic and profile patterns.
% The gnomonic projection clearly exibits the sampling issue of HEALPix.
% \TK{what issue? Commenting out for now}
Details of how the convolution kernels are plotted are described in \ref{sec:filter_visualization}.
While it is usually difficult to interpret the shape of the filters in the context of the type of data, we can notice that they often have a ``peak'' like structures.
An example of filter interpretation was demonstrated in \citep{Ribli2018learningfrom}.
% \todo{Tomek: can you say something about the filters.}
% \TK{Done}
% Nati: Note that filer are almost not evolving during the training process. It is not surprising as our architecture is likely to be overparametrized. If we want to have interpretable filters, we probably have to use a much smaller architecture.
